### 2021-05-31 talk/terms/locale_primitives.tex
Finish slides

\isacommand{locale}\isamarkupfalse%
\ algebraic{\isacharunderscore}{\kern0pt}pre{\isacharunderscore}{\kern0pt}graph\ {\isacharequal}{\kern0pt}\ \isanewline
\ \ \isakeyword{fixes}\ empty\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isacharprime}{\kern0pt}g\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymepsilon}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
\ \ \ \ \isakeyword{and}\ vertex\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}v\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g{\isachardoublequoteclose}\isanewline
\ \ \ \ \isakeyword{and}\ overlay\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isacartoucheopen}{\isasymoplus}{\isacartoucheclose}\ {\isadigit{7}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\isanewline
\ \ \ \ \isakeyword{and}\ connect\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isacartoucheopen}{\isasymrightarrow}{\isacartoucheclose}\ {\isadigit{8}}{\isadigit{0}}{\isacharparenright}{\kern0pt}

>>>>

\isacommand{locale}\isamarkupfalse%
\ algebraic{\isacharunderscore}{\kern0pt}pre{\isacharunderscore}{\kern0pt}graph\ {\isacharequal}{\kern0pt}\ \isanewline
\ \ \isakeyword{fixes}\ empty\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isacharprime}{\kern0pt}g\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymepsilon}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
\ \ \ \ \isakeyword{and}\ vertex\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}v\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g{\isachardoublequoteclose}\isanewline
\ \ \ \ \isakeyword{and}\ overlay\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isacartoucheopen}{+}{\isacartoucheclose}\ {\isadigit{7}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\isanewline
\ \ \ \ \isakeyword{and}\ connect\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isacartoucheopen}{\isasymrightarrow}{\isacartoucheclose}\ {\isadigit{8}}{\isadigit{0}}{\isacharparenright}{\kern0pt}

### 2021-05-31 talk/terms/vwalk_def.tex
Finish slides

\isacommand{inductive}\isamarkupfalse%
\ vwalk\ \isakeyword{where}\isanewline
\ \ vwalk{\isacharunderscore}{\kern0pt}Nil{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}vwalk\ g\ {\isacharbrackleft}{\kern0pt}{\isacharbrackright}{\kern0pt}{\isachardoublequoteclose}\ {\isacharbar}{\kern0pt}\isanewline
\ \ vwalk{\isacharunderscore}{\kern0pt}single{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}has{\isacharunderscore}{\kern0pt}vertex\ g\ u\ {\isasymLongrightarrow}\ vwalk\ g\ {\isacharbrackleft}{\kern0pt}u{\isacharbrackright}{\kern0pt}{\isachardoublequoteclose}\ {\isacharbar}{\kern0pt}\isanewline
\ \ vwalk{\isacharunderscore}{\kern0pt}Cons{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}vwalk\ g\ {\isacharparenleft}{\kern0pt}v{\isacharhash}{\kern0pt}xs{\isacharparenright}{\kern0pt}\ {\isasymLongrightarrow}\ has{\isacharunderscore}{\kern0pt}edge\ g\ u\ v\ {\isasymLongrightarrow}\ vwalk\ g\ {\isacharparenleft}{\kern0pt}u{\isacharhash}{\kern0pt}v{\isacharhash}{\kern0pt}xs{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline

>>>>

\isacommand{inductive}\isamarkupfalse%
\ vwalk\ \isakeyword{where}\isanewline
\ \ vwalk{\isacharunderscore}{\kern0pt}Nil{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}vwalk\ g\ {\isacharbrackleft}{\kern0pt}{\isacharbrackright}{\kern0pt}{\isachardoublequoteclose}\ {\isacharbar}{\kern0pt}\isanewline
\ \ vwalk{\isacharunderscore}{\kern0pt}single{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}has{\isacharunderscore}{\kern0pt}vertex\ g\ u\ {\isasymLongrightarrow}\ vwalk\ g\ {\isacharbrackleft}{\kern0pt}u{\isacharbrackright}{\kern0pt}{\isachardoublequoteclose}\ {\isacharbar}{\kern0pt}\isanewline
\ \ vwalk{\isacharunderscore}{\kern0pt}Cons{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}vwalk\ g\ {\isacharparenleft}{\kern0pt}v{\isacharhash}{\kern0pt}xs{\isacharparenright}{\kern0pt}\ {\isasymLongrightarrow}\ has{\isacharunderscore}{\kern0pt}edge\ g\ u\ v\ \isanewline{\isasymLongrightarrow}\ vwalk\ g\ {\isacharparenleft}{\kern0pt}u{\isacharhash}{\kern0pt}v{\isacharhash}{\kern0pt}xs{\isacharparenright}{\kern0pt}{\isachardoublequoteclose}\isanewline
